### 2020-05-07 compare_assumption.tex
done

% Created by tikzDevice version 0.12.3 on 2020-04-27 16:28:44
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 95.51, 71.16) -- (167.58, 71.16);
\definecolor{drawColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 96.55, 92.40) -- (163.42, 92.40);

\path[draw=drawColor,line width= 0.8pt,line join=round] (114.86,113.63) -- (141.83,113.63);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (164.38,134.87) -- (174.59,134.87);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 79.16,156.10) -- (149.69,156.10);

\path[draw=drawColor,line width= 0.8pt,line join=round] (152.24,177.34) -- (187.73,177.34);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.20] (105.33, 49.85) --
	(105.57, 49.84) --
	(105.81, 49.83) --
	(106.05, 49.82) --
	(106.29, 49.81) --
	(106.53, 49.80) --
	(106.77, 49.79) --
	(107.01, 49.78) --
	(107.25, 49.77) --
	(107.49, 49.76) --
	(107.73, 49.74) --
	(107.97, 49.73) --
	(108.21, 49.71) --
	(108.45, 49.69) --
	(108.69, 49.68) --
	(108.93, 49.66) --
	(109.17, 49.64) --
	(109.41, 49.62) --
	(109.65, 49.60) --
	(109.89, 49.58) --
	(110.13, 49.56) --
	(110.37, 49.54) --
	(110.61, 49.51) --
	(110.85, 49.49) --
	(111.09, 49.47) --
	(111.33, 49.45) --
	(111.57, 49.43) --
	(111.81, 49.40) --
	(112.05, 49.38) --
	(112.29, 49.36) --
	(112.53, 49.34) --
	(112.77, 49.32) --
	(113.01, 49.30) --
	(113.25, 49.28) --
	(113.49, 49.26) --
	(113.73, 49.24) --
	(113.97, 49.22) --
	(114.21, 49.20) --
	(114.45, 49.18) --
	(114.69, 49.16) --
	(114.93, 49.13) --
	(115.17, 49.11) --
	(115.41, 49.09) --
	(115.65, 49.06) --
	(115.89, 49.03) --
	(116.13, 49.00) --
	(116.37, 48.96) --
	(116.61, 48.93) --
	(116.85, 48.89) --
	(117.09, 48.84) --
	(117.33, 48.79) --
	(117.57, 48.74) --
	(117.81, 48.69) --
	(118.05, 48.63) --
	(118.29, 48.57) --
	(118.53, 48.50) --
	(118.77, 48.44) --
	(119.01, 48.37) --
	(119.25, 48.30) --
	(119.49, 48.23) --
	(119.73, 48.16) --
	(119.97, 48.08) --
	(120.21, 48.01) --
	(120.44, 47.94) --
	(120.68, 47.87) --
	(120.92, 47.80) --
	(121.16, 47.72) --
	(121.40, 47.65) --
	(121.64, 47.58) --
	(121.88, 47.51) --
	(122.12, 47.43) --
	(122.36, 47.35) --
	(122.60, 47.27) --
	(122.84, 47.18) --
	(123.08, 47.09) --
	(123.32, 47.00) --
	(123.56, 46.89) --
	(123.80, 46.79) --
	(124.04, 46.67) --
	(124.28, 46.55) --
	(124.52, 46.43) --
	(124.76, 46.30) --
	(125.00, 46.16) --
	(125.24, 46.02) --
	(125.48, 45.88) --
	(125.72, 45.73) --
	(125.96, 45.58) --
	(126.20, 45.42) --
	(126.44, 45.27) --
	(126.68, 45.11) --
	(126.92, 44.96) --
	(127.16, 44.80) --
	(127.40, 44.64) --
	(127.64, 44.49) --
	(127.88, 44.33) --
	(128.12, 44.17) --
	(128.36, 44.02) --
	(128.60, 43.86) --
	(128.84, 43.70) --
	(129.08, 43.54) --
	(129.32, 43.38) --
	(129.56, 43.22) --
	(129.80, 43.06) --
	(130.04, 42.89) --
	(130.28, 42.73) --
	(130.52, 42.56) --
	(130.76, 42.40) --
	(131.00, 42.23) --
	(131.24, 42.07) --
	(131.48, 41.90) --
	(131.72, 41.74) --
	(131.96, 41.58) --
	(132.20, 41.43) --
	(132.44, 41.27) --
	(132.68, 41.13) --
	(132.92, 40.99) --
	(133.16, 40.85) --
	(133.40, 40.72) --
	(133.64, 40.60) --
	(133.88, 40.48) --
	(134.12, 40.37) --
	(134.36, 40.26) --
	(134.60, 40.16) --
	(134.84, 40.07) --
	(135.08, 39.98) --
	(135.32, 39.90) --
	(135.56, 39.82) --
	(135.80, 39.75) --
	(136.04, 39.68) --
	(136.28, 39.61) --
	(136.52, 39.55) --
	(136.76, 39.50) --
	(137.00, 39.45) --
	(137.24, 39.41) --
	(137.48, 39.38) --
	(137.72, 39.35) --
	(137.96, 39.33) --
	(138.20, 39.32) --
	(138.44, 39.31) --
	(138.68, 39.32) --
	(138.92, 39.32) --
	(139.16, 39.34) --
	(139.40, 39.37) --
	(139.64, 39.40) --
	(139.88, 39.44) --
	(140.12, 39.49) --
	(140.36, 39.54) --
	(140.60, 39.60) --
	(140.84, 39.67) --
	(141.08, 39.74) --
	(141.32, 39.82) --
	(141.56, 39.90) --
	(141.80, 39.99) --
	(142.04, 40.08) --
	(142.28, 40.18) --
	(142.52, 40.29) --
	(142.76, 40.40) --
	(143.00, 40.51) --
	(143.24, 40.62) --
	(143.48, 40.75) --
	(143.72, 40.87) --
	(143.96, 40.99) --
	(144.20, 41.12) --
	(144.44, 41.25) --
	(144.68, 41.38) --
	(144.92, 41.51) --
	(145.16, 41.65) --
	(145.40, 41.77) --
	(145.64, 41.90) --
	(145.88, 42.03) --
	(146.12, 42.15) --
	(146.36, 42.26) --
	(146.60, 42.38) --
	(146.84, 42.49) --
	(147.08, 42.59) --
	(147.32, 42.69) --
	(147.56, 42.79) --
	(147.80, 42.88) --
	(148.04, 42.97) --
	(148.28, 43.05) --
	(148.52, 43.13) --
	(148.76, 43.21) --
	(149.00, 43.29) --
	(149.24, 43.37) --
	(149.48, 43.45) --
	(149.72, 43.53) --
	(149.96, 43.61) --
	(150.20, 43.70) --
	(150.44, 43.78) --
	(150.68, 43.86) --
	(150.92, 43.95) --
	(151.16, 44.04) --
	(151.40, 44.13) --
	(151.64, 44.22) --
	(151.88, 44.32) --
	(152.12, 44.41) --
	(152.36, 44.52) --
	(152.60, 44.62) --
	(152.84, 44.72) --
	(153.08, 44.83) --
	(153.32, 44.94) --
	(153.56, 45.06) --
	(153.80, 45.18) --
	(154.04, 45.30) --
	(154.28, 45.42) --
	(154.52, 45.54) --
	(154.76, 45.67) --
	(155.00, 45.80) --
	(155.24, 45.92) --
	(155.48, 46.05) --
	(155.72, 46.18) --
	(155.96, 46.30) --
	(156.20, 46.42) --
	(156.44, 46.53) --
	(156.68, 46.65) --
	(156.92, 46.75) --
	(157.16, 46.85) --
	(157.40, 46.95) --
	(157.64, 47.04) --
	(157.88, 47.12) --
	(158.12, 47.20) --
	(158.36, 47.27) --
	(158.60, 47.34) --
	(158.84, 47.40) --
	(159.08, 47.45) --
	(159.32, 47.50) --
	(159.56, 47.55) --
	(159.80, 47.59) --
	(160.04, 47.62) --
	(160.28, 47.66) --
	(160.52, 47.69) --
	(160.76, 47.71) --
	(161.00, 47.74) --
	(161.24, 47.76) --
	(161.48, 47.78) --
	(161.72, 47.81) --
	(161.96, 47.83) --
	(162.20, 47.85) --
	(162.44, 47.88) --
	(162.68, 47.91) --
	(162.92, 47.94) --
	(163.16, 47.97) --
	(163.40, 48.01) --
	(163.64, 48.05) --
	(163.88, 48.09) --
	(164.12, 48.13) --
	(164.36, 48.18) --
	(164.60, 48.22) --
	(164.84, 48.27) --
	(165.08, 48.32) --
	(165.32, 48.36) --
	(165.56, 48.41) --
	(165.80, 48.46) --
	(166.04, 48.50) --
	(166.28, 48.54) --
	(166.52, 48.59) --
	(166.76, 48.63) --
	(167.00, 48.66) --
	(167.24, 48.70) --
	(167.48, 48.74) --
	(167.72, 48.77) --
	(167.96, 48.81) --
	(168.20, 48.84) --
	(168.44, 48.88) --
	(168.68, 48.91) --
	(168.92, 48.95) --
	(169.16, 48.98) --
	(169.40, 49.01) --
	(169.64, 49.05) --
	(169.88, 49.08) --
	(170.12, 49.11) --
	(170.36, 49.14) --
	(170.60, 49.17) --
	(170.84, 49.20) --
	(171.08, 49.22) --
	(171.32, 49.25) --
	(171.56, 49.27) --
	(171.80, 49.29) --
	(172.04, 49.31) --
	(172.28, 49.33) --
	(172.52, 49.34) --
	(172.76, 49.36) --
	(173.00, 49.37) --
	(173.24, 49.38) --
	(173.48, 49.39) --
	(173.72, 49.41) --
	(173.96, 49.42) --
	(174.20, 49.43) --
	(174.44, 49.44) --
	(174.68, 49.45) --
	(174.92, 49.46) --
	(175.16, 49.47) --
	(175.40, 49.48) --
	(175.64, 49.49) --
	(175.88, 49.50) --
	(176.12, 49.51) --
	(176.36, 49.52) --
	(176.60, 49.53) --
	(176.84, 49.53) --
	(177.08, 49.54) --
	(177.32, 49.55) --
	(177.56, 49.55) --
	(177.80, 49.56) --
	(178.04, 49.56) --
	(178.28, 49.57) --
	(178.52, 49.58) --
	(178.76, 49.58) --
	(179.00, 49.59) --
	(179.24, 49.59) --
	(179.48, 49.60) --
	(179.72, 49.60) --
	(179.96, 49.61) --
	(180.20, 49.62) --
	(180.44, 49.63) --
	(180.68, 49.64) --
	(180.92, 49.65) --
	(181.16, 49.66) --
	(181.40, 49.67) --
	(181.64, 49.68) --
	(181.88, 49.69) --
	(182.12, 49.70) --
	(182.36, 49.72) --
	(182.60, 49.73) --
	(182.84, 49.74) --
	(183.08, 49.75) --
	(183.32, 49.76) --
	(183.56, 49.77) --
	(183.80, 49.78) --
	(184.04, 49.79) --
	(184.28, 49.80) --
	(184.52, 49.81) --
	(184.76, 49.81) --
	(185.00, 49.82) --
	(185.24, 49.82) --
	(185.48, 49.83) --
	(185.72, 49.83) --
	(185.96, 49.83) --
	(186.20, 49.83) --
	(186.44, 49.83) --
	(186.68, 49.83) --
	(186.92, 49.83) --
	(187.16, 49.83) --
	(187.40, 49.83) --
	(187.64, 49.83) --
	(187.88, 49.82) --
	(188.12, 49.82) --
	(188.36, 49.82) --
	(188.60, 49.82) --
	(188.84, 49.81) --
	(189.08, 49.81) --
	(189.32, 49.81) --
	(189.56, 49.81) --
	(189.80, 49.81) --
	(190.04, 49.81) --
	(190.28, 49.81) --
	(190.52, 49.81) --
	(190.76, 49.81) --
	(191.00, 49.81) --
	(191.24, 49.81) --
	(191.48, 49.82) --
	(191.72, 49.82) --
	(191.96, 49.82) --
	(192.20, 49.83) --
	(192.44, 49.83) --
	(192.68, 49.84) --
	(192.92, 49.84) --
	(193.16, 49.85) --
	(193.40, 49.86) --
	(193.64, 49.86) --
	(193.88, 49.87) --
	(194.12, 49.87) --
	(194.36, 49.87) --
	(194.60, 49.88) --
	(194.84, 49.88) --
	(195.08, 49.88) --
	(195.32, 49.88) --
	(195.56, 49.88) --
	(195.80, 49.88) --
	(196.04, 49.88) --
	(196.28, 49.88) --
	(196.52, 49.88) --
	(196.76, 49.88) --
	(197.00, 49.88) --
	(197.24, 49.88) --
	(197.48, 49.88) --
	(197.72, 49.88) --
	(197.96, 49.88) --
	(198.20, 49.88) --
	(198.44, 49.88) --
	(198.68, 49.88) --
	(198.92, 49.88) --
	(199.16, 49.88) --
	(199.40, 49.89) --
	(199.64, 49.89) --
	(199.88, 49.89) --
	(200.12, 49.89) --
	(200.36, 49.90) --
	(200.60, 49.90) --
	(200.84, 49.90) --
	(201.08, 49.91) --
	(201.32, 49.91) --
	(201.56, 49.91) --
	(201.80, 49.91) --
	(202.04, 49.92) --
	(202.28, 49.92) --
	(202.52, 49.92) --
	(202.76, 49.92) --
	(203.00, 49.92) --

@@

	(209.72, 49.92) --
	(209.96, 49.92) --
	(210.20, 49.92) --
	(210.44, 49.92) --
	(210.68, 49.92) --
	(210.92, 49.92) --
	(211.16, 49.92) --
	(211.40, 49.91) --
	(211.64, 49.91) --
	(211.88, 49.91) --
	(212.12, 49.91) --
	(212.36, 49.91) --
	(212.60, 49.91) --
	(212.84, 49.91) --
	(213.08, 49.91) --
	(213.32, 49.91) --
	(213.56, 49.90) --
	(213.80, 49.90) --
	(214.04, 49.90) --
	(214.28, 49.91) --
	(214.52, 49.91) --
	(214.76, 49.91) --
	(215.00, 49.91) --
	(215.24, 49.91) --
	(215.48, 49.91) --
	(215.72, 49.91) --
	(215.96, 49.91) --
	(216.20, 49.92) --
	(216.44, 49.92) --
	(216.68, 49.92) --
	(216.92, 49.92) --
	(217.16, 49.92) --
	(217.40, 49.92) --
	(217.64, 49.92) --

@@

	(224.12, 49.92) --
	(224.36, 49.92) --
	(224.60, 49.92) --
	(224.84, 49.92) --
	(225.08, 49.92) --
	(225.32, 49.92) --
	(225.56, 49.92) --
	(225.80, 49.91) --
	(226.04, 49.91) --
	(226.28, 49.91) --
	(226.52, 49.91) --
	(226.76, 49.91) --
	(227.00, 49.91) --
	(227.24, 49.91) --
	(227.48, 49.91) --
	(227.72, 49.90) --
	(227.96, 49.90) --

@@

	(105.33, 49.85) --

@@

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (320.06,198.12) -- (393.26,198.12);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (340.83,154.14) -- (468.86,154.14);

\path[draw=drawColor,line width= 0.8pt,line join=round] (349.40,176.13) -- (364.04,176.13);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.20] (327.85, 44.18) --
	(328.07, 44.18) --
	(328.28, 44.18) --
	(328.50, 44.18) --
	(328.72, 44.18) --
	(328.93, 44.18) --
	(329.15, 44.18) --
	(329.36, 44.17) --
	(329.58, 44.17) --
	(329.79, 44.17) --
	(330.01, 44.17) --
	(330.23, 44.16) --
	(330.44, 44.16) --
	(330.66, 44.16) --
	(330.87, 44.15) --
	(331.09, 44.15) --
	(331.30, 44.14) --
	(331.52, 44.14) --
	(331.74, 44.13) --
	(331.95, 44.13) --

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-07 17:10:16
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (167.58, 71.16) --
	(167.58, 71.16);

\path[draw=drawColor,line width= 0.8pt,line join=round] (167.58, 71.16) --
	( 95.51, 71.16);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 95.51, 71.16) --
	( 95.51, 71.16);
\definecolor{drawColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.8pt,line join=round] (163.42, 92.40) --
	(163.42, 92.40);

\path[draw=drawColor,line width= 0.8pt,line join=round] (163.42, 92.40) --
	( 96.55, 92.40);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 96.55, 92.40) --
	( 96.55, 92.40);

\path[draw=drawColor,line width= 0.8pt,line join=round] (141.83,113.63) --
	(141.83,113.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (141.83,113.63) --
	(114.86,113.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (114.86,113.63) --
	(114.86,113.63);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.8pt,line join=round] (117.88,198.57) --
	(117.88,198.57);

\path[draw=drawColor,line width= 0.8pt,line join=round] (117.88,198.57) --
	(117.88,198.57);

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (174.59,134.87) --
	(174.59,134.87);

\path[draw=drawColor,line width= 0.8pt,line join=round] (174.59,134.87) --
	(164.38,134.87);

\path[draw=drawColor,line width= 0.8pt,line join=round] (164.38,134.87) --
	(164.38,134.87);

\path[draw=drawColor,line width= 0.8pt,line join=round] (149.69,156.10) --
	(149.69,156.10);

\path[draw=drawColor,line width= 0.8pt,line join=round] (149.69,156.10) --
	( 79.16,156.10);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 79.16,156.10) --
	( 79.16,156.10);

\path[draw=drawColor,line width= 0.8pt,line join=round] (187.73,177.34) --
	(187.73,177.34);

\path[draw=drawColor,line width= 0.8pt,line join=round] (187.73,177.34) --
	(152.24,177.34);

\path[draw=drawColor,line width= 0.8pt,line join=round] (152.24,177.34) --
	(152.24,177.34);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.20] (105.33, 49.93) --
	(105.57, 49.93) --
	(105.81, 49.93) --
	(106.05, 49.93) --
	(106.29, 49.93) --
	(106.53, 49.93) --
	(106.77, 49.93) --
	(107.01, 49.93) --
	(107.25, 49.93) --
	(107.49, 49.93) --
	(107.73, 49.93) --
	(107.97, 49.93) --
	(108.21, 49.93) --
	(108.45, 49.93) --
	(108.69, 49.93) --
	(108.93, 49.93) --
	(109.17, 49.93) --
	(109.41, 49.93) --
	(109.65, 49.93) --
	(109.89, 49.93) --
	(110.13, 49.93) --
	(110.37, 49.93) --
	(110.61, 49.93) --
	(110.85, 49.93) --
	(111.09, 49.93) --
	(111.33, 49.93) --
	(111.57, 49.93) --
	(111.81, 49.93) --
	(112.05, 49.93) --
	(112.29, 49.93) --
	(112.53, 49.93) --
	(112.77, 49.93) --
	(113.01, 49.93) --
	(113.25, 49.93) --
	(113.49, 49.93) --
	(113.73, 49.93) --
	(113.97, 49.93) --
	(114.21, 49.93) --
	(114.45, 49.93) --
	(114.69, 49.93) --
	(114.93, 49.93) --
	(115.17, 49.93) --
	(115.41, 49.93) --
	(115.65, 49.93) --
	(115.89, 49.93) --
	(116.13, 49.93) --
	(116.37, 49.93) --
	(116.61, 49.93) --
	(116.85, 49.93) --
	(117.09, 49.93) --
	(117.33, 49.93) --
	(117.57, 49.93) --
	(117.81, 49.93) --
	(118.05, 49.93) --
	(118.29, 49.93) --
	(118.53, 49.93) --
	(118.77, 49.93) --
	(119.01, 49.93) --
	(119.25, 49.93) --
	(119.49, 49.93) --
	(119.73, 49.93) --
	(119.97, 49.93) --
	(120.21, 49.93) --
	(120.44, 49.93) --
	(120.68, 49.93) --
	(120.92, 49.93) --
	(121.16, 49.93) --
	(121.40, 49.93) --
	(121.64, 49.93) --
	(121.88, 49.93) --
	(122.12, 49.93) --
	(122.36, 49.93) --
	(122.60, 49.93) --
	(122.84, 49.93) --
	(123.08, 49.93) --
	(123.32, 49.93) --
	(123.56, 49.93) --
	(123.80, 49.93) --
	(124.04, 49.93) --
	(124.28, 49.93) --
	(124.52, 49.93) --
	(124.76, 49.93) --
	(125.00, 49.93) --
	(125.24, 49.93) --
	(125.48, 49.93) --
	(125.72, 49.93) --
	(125.96, 49.93) --
	(126.20, 49.93) --
	(126.44, 49.93) --
	(126.68, 49.93) --
	(126.92, 49.93) --
	(127.16, 49.93) --
	(127.40, 49.93) --
	(127.64, 49.93) --
	(127.88, 49.93) --
	(128.12, 49.93) --
	(128.36, 49.93) --
	(128.60, 49.93) --
	(128.84, 49.93) --
	(129.08, 49.93) --
	(129.32, 49.93) --
	(129.56, 49.93) --
	(129.80, 49.93) --
	(130.04, 49.93) --
	(130.28, 49.93) --
	(130.52, 49.93) --
	(130.76, 49.93) --
	(131.00, 49.93) --
	(131.24, 49.93) --
	(131.48, 49.93) --
	(131.72, 49.93) --
	(131.96, 49.93) --
	(132.20, 49.93) --
	(132.44, 49.93) --
	(132.68, 49.93) --
	(132.92, 49.93) --
	(133.16, 49.93) --
	(133.40, 49.93) --
	(133.64, 49.93) --
	(133.88, 49.93) --
	(134.12, 49.93) --
	(134.36, 49.93) --
	(134.60, 49.93) --
	(134.84, 49.93) --
	(135.08, 49.93) --
	(135.32, 49.93) --
	(135.56, 49.93) --
	(135.80, 49.93) --
	(136.04, 49.93) --
	(136.28, 49.93) --
	(136.52, 49.93) --
	(136.76, 49.93) --
	(137.00, 49.93) --
	(137.24, 49.93) --
	(137.48, 49.93) --
	(137.72, 49.93) --
	(137.96, 49.93) --
	(138.20, 49.93) --
	(138.44, 49.93) --
	(138.68, 49.93) --
	(138.92, 49.93) --
	(139.16, 49.93) --
	(139.40, 49.93) --
	(139.64, 49.93) --
	(139.88, 49.93) --
	(140.12, 49.93) --
	(140.36, 49.93) --
	(140.60, 49.93) --
	(140.84, 49.93) --
	(141.08, 49.93) --
	(141.32, 49.93) --
	(141.56, 49.93) --
	(141.80, 49.93) --
	(142.04, 49.93) --
	(142.28, 49.93) --
	(142.52, 49.93) --
	(142.76, 49.93) --
	(143.00, 49.93) --
	(143.24, 49.93) --
	(143.48, 49.93) --
	(143.72, 49.93) --
	(143.96, 49.93) --
	(144.20, 49.93) --
	(144.44, 49.93) --
	(144.68, 49.93) --
	(144.92, 49.93) --
	(145.16, 49.93) --
	(145.40, 49.93) --
	(145.64, 49.93) --
	(145.88, 49.93) --
	(146.12, 49.93) --
	(146.36, 49.93) --
	(146.60, 49.93) --
	(146.84, 49.93) --
	(147.08, 49.93) --
	(147.32, 49.93) --
	(147.56, 49.93) --
	(147.80, 49.93) --
	(148.04, 49.93) --
	(148.28, 49.93) --
	(148.52, 49.93) --
	(148.76, 49.93) --
	(149.00, 49.93) --
	(149.24, 49.93) --
	(149.48, 49.93) --
	(149.72, 49.93) --
	(149.96, 49.93) --
	(150.20, 49.93) --
	(150.44, 49.93) --
	(150.68, 49.93) --
	(150.92, 49.93) --
	(151.16, 49.93) --
	(151.40, 49.93) --
	(151.64, 49.93) --
	(151.88, 49.93) --
	(152.12, 49.93) --
	(152.36, 49.93) --
	(152.60, 49.93) --
	(152.84, 49.93) --
	(153.08, 49.93) --
	(153.32, 49.93) --
	(153.56, 49.93) --
	(153.80, 49.93) --
	(154.04, 49.93) --
	(154.28, 49.93) --
	(154.52, 49.93) --
	(154.76, 49.93) --
	(155.00, 49.93) --
	(155.24, 49.93) --
	(155.48, 49.93) --
	(155.72, 49.93) --
	(155.96, 49.93) --
	(156.20, 49.93) --
	(156.44, 49.93) --
	(156.68, 49.93) --
	(156.92, 49.93) --
	(157.16, 49.93) --
	(157.40, 49.93) --
	(157.64, 49.93) --
	(157.88, 49.93) --
	(158.12, 49.93) --
	(158.36, 49.93) --
	(158.60, 49.93) --
	(158.84, 49.93) --
	(159.08, 49.93) --
	(159.32, 49.93) --
	(159.56, 49.93) --
	(159.80, 49.93) --
	(160.04, 49.93) --
	(160.28, 49.93) --
	(160.52, 49.93) --
	(160.76, 49.93) --
	(161.00, 49.93) --
	(161.24, 49.93) --
	(161.48, 49.93) --
	(161.72, 49.93) --
	(161.96, 49.93) --
	(162.20, 49.93) --
	(162.44, 49.93) --
	(162.68, 49.93) --
	(162.92, 49.93) --
	(163.16, 49.93) --
	(163.40, 49.93) --
	(163.64, 49.93) --
	(163.88, 49.93) --
	(164.12, 49.93) --
	(164.36, 49.93) --
	(164.60, 49.93) --
	(164.84, 49.93) --
	(165.08, 49.93) --
	(165.32, 49.93) --
	(165.56, 49.93) --
	(165.80, 49.93) --
	(166.04, 49.93) --
	(166.28, 49.93) --
	(166.52, 49.93) --
	(166.76, 49.93) --
	(167.00, 49.93) --
	(167.24, 49.93) --
	(167.48, 49.93) --
	(167.72, 49.93) --
	(167.96, 49.93) --
	(168.20, 49.93) --
	(168.44, 49.93) --
	(168.68, 49.93) --
	(168.92, 49.93) --
	(169.16, 49.93) --
	(169.40, 49.93) --
	(169.64, 49.93) --
	(169.88, 49.93) --
	(170.12, 49.93) --
	(170.36, 49.93) --
	(170.60, 49.93) --
	(170.84, 49.93) --
	(171.08, 49.93) --
	(171.32, 49.93) --
	(171.56, 49.93) --
	(171.80, 49.93) --
	(172.04, 49.93) --
	(172.28, 49.93) --
	(172.52, 49.93) --
	(172.76, 49.93) --
	(173.00, 49.93) --
	(173.24, 49.93) --
	(173.48, 49.93) --
	(173.72, 49.93) --
	(173.96, 49.93) --
	(174.20, 49.93) --
	(174.44, 49.93) --
	(174.68, 49.93) --
	(174.92, 49.93) --
	(175.16, 49.93) --
	(175.40, 49.93) --
	(175.64, 49.93) --
	(175.88, 49.93) --
	(176.12, 49.93) --
	(176.36, 49.93) --
	(176.60, 49.93) --
	(176.84, 49.93) --
	(177.08, 49.93) --
	(177.32, 49.93) --
	(177.56, 49.93) --
	(177.80, 49.93) --
	(178.04, 49.93) --
	(178.28, 49.93) --
	(178.52, 49.93) --
	(178.76, 49.93) --
	(179.00, 49.93) --
	(179.24, 49.93) --
	(179.48, 49.93) --
	(179.72, 49.93) --
	(179.96, 49.93) --
	(180.20, 49.93) --
	(180.44, 49.93) --
	(180.68, 49.93) --
	(180.92, 49.93) --
	(181.16, 49.93) --
	(181.40, 49.93) --
	(181.64, 49.93) --
	(181.88, 49.93) --
	(182.12, 49.93) --
	(182.36, 49.93) --
	(182.60, 49.93) --
	(182.84, 49.93) --
	(183.08, 49.93) --
	(183.32, 49.93) --
	(183.56, 49.93) --
	(183.80, 49.93) --
	(184.04, 49.93) --
	(184.28, 49.93) --
	(184.52, 49.93) --
	(184.76, 49.93) --
	(185.00, 49.93) --
	(185.24, 49.93) --
	(185.48, 49.93) --
	(185.72, 49.93) --
	(185.96, 49.93) --
	(186.20, 49.93) --
	(186.44, 49.93) --
	(186.68, 49.93) --
	(186.92, 49.93) --
	(187.16, 49.93) --
	(187.40, 49.93) --
	(187.64, 49.93) --
	(187.88, 49.93) --
	(188.12, 49.93) --
	(188.36, 49.93) --
	(188.60, 49.93) --
	(188.84, 49.93) --
	(189.08, 49.93) --
	(189.32, 49.93) --
	(189.56, 49.93) --
	(189.80, 49.93) --
	(190.04, 49.93) --
	(190.28, 49.93) --
	(190.52, 49.93) --
	(190.76, 49.93) --
	(191.00, 49.93) --
	(191.24, 49.93) --
	(191.48, 49.93) --
	(191.72, 49.93) --
	(191.96, 49.93) --
	(192.20, 49.93) --
	(192.44, 49.93) --
	(192.68, 49.93) --
	(192.92, 49.93) --
	(193.16, 49.93) --
	(193.40, 49.93) --
	(193.64, 49.93) --
	(193.88, 49.93) --
	(194.12, 49.93) --
	(194.36, 49.93) --
	(194.60, 49.93) --
	(194.84, 49.93) --
	(195.08, 49.93) --
	(195.32, 49.93) --
	(195.56, 49.93) --
	(195.80, 49.93) --
	(196.04, 49.93) --
	(196.28, 49.93) --
	(196.52, 49.93) --
	(196.76, 49.93) --
	(197.00, 49.93) --
	(197.24, 49.93) --
	(197.48, 49.93) --
	(197.72, 49.93) --
	(197.96, 49.93) --
	(198.20, 49.93) --
	(198.44, 49.93) --
	(198.68, 49.93) --
	(198.92, 49.93) --
	(199.16, 49.93) --
	(199.40, 49.93) --
	(199.64, 49.93) --
	(199.88, 49.93) --
	(200.12, 49.93) --
	(200.36, 49.93) --
	(200.60, 49.93) --
	(200.84, 49.93) --
	(201.08, 49.93) --
	(201.32, 49.93) --
	(201.56, 49.93) --
	(201.80, 49.93) --
	(202.04, 49.93) --
	(202.28, 49.93) --
	(202.52, 49.93) --
	(202.76, 49.93) --
	(203.00, 49.93) --

@@

	(209.72, 49.93) --
	(209.96, 49.93) --
	(210.20, 49.93) --
	(210.44, 49.93) --
	(210.68, 49.93) --
	(210.92, 49.93) --
	(211.16, 49.93) --
	(211.40, 49.93) --
	(211.64, 49.93) --
	(211.88, 49.93) --
	(212.12, 49.93) --
	(212.36, 49.93) --
	(212.60, 49.93) --
	(212.84, 49.93) --
	(213.08, 49.93) --
	(213.32, 49.93) --
	(213.56, 49.93) --
	(213.80, 49.93) --
	(214.04, 49.93) --
	(214.28, 49.93) --
	(214.52, 49.93) --
	(214.76, 49.93) --
	(215.00, 49.93) --
	(215.24, 49.93) --
	(215.48, 49.93) --
	(215.72, 49.93) --
	(215.96, 49.93) --
	(216.20, 49.93) --
	(216.44, 49.93) --
	(216.68, 49.93) --
	(216.92, 49.93) --
	(217.16, 49.93) --
	(217.40, 49.93) --
	(217.64, 49.93) --

@@

	(224.12, 49.93) --
	(224.36, 49.93) --
	(224.60, 49.93) --
	(224.84, 49.93) --
	(225.08, 49.93) --
	(225.32, 49.93) --
	(225.56, 49.93) --
	(225.80, 49.93) --
	(226.04, 49.93) --
	(226.28, 49.93) --
	(226.52, 49.93) --
	(226.76, 49.93) --
	(227.00, 49.93) --
	(227.24, 49.93) --
	(227.48, 49.93) --
	(227.72, 49.93) --
	(227.96, 49.93) --

@@

	(105.33, 49.93) --

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (364.41,110.17) --
	(364.41,110.17);

\path[draw=drawColor,line width= 0.8pt,line join=round] (364.41,110.17) --
	(364.41,110.17);

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (393.26,198.12) --
	(393.26,198.12);

\path[draw=drawColor,line width= 0.8pt,line join=round] (393.26,198.12) --
	(320.06,198.12);

\path[draw=drawColor,line width= 0.8pt,line join=round] (320.06,198.12) --
	(320.06,198.12);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.8pt,line join=round] (349.00,132.16) --
	(349.00,132.16);

\path[draw=drawColor,line width= 0.8pt,line join=round] (349.00,132.16) --
	(349.00,132.16);

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (468.86,154.14) --
	(468.86,154.14);

\path[draw=drawColor,line width= 0.8pt,line join=round] (468.86,154.14) --
	(340.83,154.14);

\path[draw=drawColor,line width= 0.8pt,line join=round] (340.83,154.14) --
	(340.83,154.14);

\path[draw=drawColor,line width= 0.8pt,line join=round] (364.04,176.13) --
	(364.04,176.13);

\path[draw=drawColor,line width= 0.8pt,line join=round] (364.04,176.13) --
	(349.40,176.13);

\path[draw=drawColor,line width= 0.8pt,line join=round] (349.40,176.13) --
	(349.40,176.13);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.20] (327.85, 44.21) --
	(328.07, 44.21) --
	(328.28, 44.21) --
	(328.50, 44.21) --
	(328.72, 44.21) --
	(328.93, 44.21) --
